### 2022-11-02 draft/draft.Rmd
fixed typo

```{r hierarchy, results = 'asis'}
blockmodel.df <- dplyr::tibble(
  Model = c('SBM', 'DCBM', 'PABM'),
  Parameters = c('$K (K-1) / 2$', '$K (K-1) / 2 + n$', '$n K$'),
  Dimension = c('$K$', '$K$', '$K^2$'),
  `Matrix Decomposition` = c('$P = Z B Z^\\top$', '$P = (\\Omega Z) B (\\Omega Z)^\\top$', '$P = X \\Pi X^\\top$'),
  `Reduction to simpler model` = c('', '$\\omega = e$', '$\\lambda_{ik} = \\omega_i \\sqrt{\\theta_{z_i, k}}$')
)
knitr::kable(blockmodel.df, 'latex', 
             escape = FALSE,
             caption = 'Summary of an hierarchical or nested view of block momdels.')
```

>>>>

```{r hierarchy, results = 'asis'}
blockmodel.df <- dplyr::tibble(
  Model = c('SBM', 'DCBM', 'PABM'),
  Parameters = c('$K (K-1) / 2$', '$K (K-1) / 2 + n$', '$n K$'),
  `$\\mathrm{rank}(P)$` = c('$K$', '$K$', '$K^2$'),
  `Matrix Decomposition` = c('$P = Z B Z^\\top$', '$P = (\\Omega Z) B (\\Omega Z)^\\top$', '$P = X \\Pi X^\\top$'),
  `Reduction to simpler model` = c('', '$\\omega = e$', '$\\lambda_{ik} = \\omega_i \\sqrt{\\theta_{z_i, k}}$')
)
knitr::kable(blockmodel.df, 'latex', 
             escape = FALSE,
             caption = 'Summary of an hierarchical or nested view of block momdels.')
```
